### 2012-08-24 doc/me699/proposal/me699_proposal.tex
updates to me699 proposal
finished 699 proposal

where $\ve{I}$ is the identity matrix, $\mu$ is the dynamic
viscosityof the fluid, and $\kappa$ is the thermal conductivity of the
fluid. These fluid properties will be assumed constant and boundary
conditions will be chosen as a combination of Neumann and Dirichlet
conditions depending on the problem chosen.

\subsection{Discretization}
Reference \cite{shadid_1997} uses a pressure stabilized
Petrov-Galerkin finite element formulation of these equations
\cite{hughes_1986}. Depending on the software infrastructure
developed, these may or may not be as easy to formulate as the finite
volume discretizations in \cite{mchugh_1994} due to the availabilty of
finite element discretization libraries, finite element assembly
engines, and unstructured mesh databases available in the Trilinos
scientific computing libraries \cite{trilinos_2005}. It will likely be
easiest to start with the finite volume approach.

\subsection{Solution Method}
We will choose an inexact Newton method for the nonlinear scheme solve
these equations \cite{dembo_1982}. Of particular interest will be
investigating how the forcing term affects convergence of the
nonlinear resdiual \cite{eisenstat_1996}. In addition, if convergence
issues are noted, globalization methods may be investigated to improve
the Newton correction \cite{pawlowski_2006}. The linear solver for the
Newton method will be GMRES as its convergence properties for these
types of systems are well documented \cite{saad_1986}. We will seek to
solve these equations using parallel methods provided by well
established framework libraries provided by the Trilinos suite of
scientific computing libraries \cite{trilinos_2005}.

\subsection{Benchmark Problems}
To verify the implementation, three widely reference two-dimensional
benchmark problems will be assessed using the resulting software. The
natural convection cavity problem \cite{davis_1983}, the driven cavity
problem \cite{ghia_1982}, and flow over a backwards step
\cite{gartling_1990}.

>>>>

where $\ve{I}$ is the identity matrix, $\mu$ is the dynamic
viscosity of the fluid, and $\kappa$ is the thermal conductivity of the
fluid. These fluid properties will be assumed constant and boundary
conditions will be chosen as a combination of Neumann and Dirichlet
conditions depending on the problem chosen.

\subsection{Discretization}
Reference \cite{shadid_1997} uses a pressure stabilized
Petrov-Galerkin finite element formulation of these equations
\cite{hughes_1986}. Depending on the software infrastructure
developed, these may or may not be as easy to formulate as the finite
volume discretizations in \cite{mchugh_1994} due to the availabilty of
finite element discretization libraries, finite element assembly
engines, and unstructured mesh databases in the Trilinos scientific
computing libraries \cite{trilinos_2005}. It will likely be easiest to
start with the finite volume approach.

\subsection{Solution Method}
We will choose an inexact Newton method for the nonlinear scheme to
solve these equations \cite{dembo_1982}. Of particular interest will
be investigating how the forcing term affects convergence of the
nonlinear resdiual \cite{eisenstat_1996}. In addition, if convergence
issues are noted, globalization methods may be investigated to improve
the Newton correction \cite{pawlowski_2006}. The linear solver for the
Newton method will be GMRES \cite{saad_1986} as its convergence
properties for these types of systems are well documented and its long
recurrence relation has been shown to improve robustness and preserve
a monotonically decreasing residuals in nonlinear solves. We will seek
to solve these equations using parallel methods provided by well
established framework libraries in the Trilinos suite of scientific
computing libraries \cite{trilinos_2005}.

\subsection{Benchmark Problems}
To verify the implementation, three widely referenced two-dimensional
benchmark problems will be assessed using the resulting software. The
natural convection cavity problem \cite{davis_1983}, the driven cavity
problem \cite{ghia_1982}, and flow over a backwards step
\cite{gartling_1990}.
